---
title: "R Notebook"
output: html_notebook
---

# Exercise 1:

```{r package, message=FALSE, cache=FALSE}
library("tidyverse")
library("testthat")
library("ggplot2")
```

```{r}
gap_5060 <- read_csv("data/gapminder-5060.csv")
```

#### 2. Visualize life expectancy over time for Canada in the 1950s and 1960s using a line plot.
  
```{r}
# Filter the data for Canada only
gap_5060_CA <- gap_5060 %>%
  filter(country == "Canada")
# Visualize
ggplot(data = gap_5060_CA, aes(x = year, y = lifeExp)) +
  geom_line()
```

# Exercise 3: Organization

Devise a naming scheme for files:
 1. Assays performed on different days
 2. BRAF mRNA
 3. Different plasmids were used to transform e. coli (Plasmid CL56)
 4. Readings from plate containing multiple wells:
   * rows (eg A, B. C)
   * Cols (eg 1 ,2, 3)
   * 1 CSV per well

BRAF_$isodatetime_$row_$col_$plasmid.csv

```{r}

filename <- function (experiment, experiment_type, iso_date, culture, sample, plasmid) {
  paste(paste(experiment, experiment_type, iso_date, row, col, plasmid, sep="_"), ".csv", sep="")
}

filename('mRNA', 'BRAFAssay', 20170101, "A", "1", "CL56")

```




